Supplementary materials

### 2018-02-22 publication/manuscript.Rmd
Enable cross referencing accross tex files
This one took a while...

---
title: "Pollen competition"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
bibliography: references.bib
csl: ecology-letters.csl
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
---

@@

Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table S1). 
When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table S2; Figure S1 and S2). 
Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table S3).

>>>>

---
title: "Pollen competition"
author: "Fernando Cagua, Hugo Marrero, Jason Tylianakis, Daniel Stouffer"
bibliography: references.bib
csl: ecology-letters.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument{supp_info}
---

@@

Over all study sites, we found that `r round(prop_sig_global*100)`% of species observed a significant increasse (at the $\alpha = 0.05$ level) in pollen density when comparing open and bagged flowers (Table \@ref(tab:table-species-gain-global)). 
When looking at the differences within sites, we found that only `r round(prop_consistency*100)`% of the species that were present in more than one site had the same response across community (Table \@ref(tab:table-species-gain-site); Figure \@ref(fig:fig-conspecific-per-site) and \@ref(fig:fig-conspecific-per-plant)). 
Despite these differences, the community had a comparatively small effect on wether animal pollination increased the pollen density or not (Table \@ref(tab:table-variation-across-sites)).

### 2018-02-22 publication/supp_info.Rmd
Enable cross referencing accross tex files
This one took a while...

---
title: "Supplementary materials"
author: "Fernando Cagua"
output: pdf_document
header-includes:
  - \usepackage{booktabs}
---

@@

```{r table species gain global, results = 'asis'}
loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_global) %>%
  select(recipient, estimate, statistic, p.value) %>%
  mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient) %>%
  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the species level (across communities).") %>%
  print.xtable(sanitize.text.function = function(x) x)
```

```{r table species gain site, results = 'asis'}
loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_site) %>%
  inner_join(sites, by = "site_name") %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name)) %>%
  filter(n_sites > 1) %>%
  group_by() %>%
  mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  select(recipient, site_name, estimate, statistic, p.value) %>%
  rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient, 
         `community` = site_name) %>%
  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the community level. Only species present in more than one community are shown.") %>%
  print(sanitize.text.function = function(x) x)
```

```{r variation across sites, results='asis'}
loadd(consp_self)
consp_self %>%
  anova(test = "Chisq")  %>%
  xtable(caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.')
```

```{r plot conspecific per site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
loadd(dep_frame, sites)
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

```{r plot conspecific per plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species. Only species present in more than onse site are shown. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name), 
         site_name = `str_sub<-`(site_name, 1, 3, ''), 
         site_name = str_replace_all(site_name, '_', ' - ')) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

```{r abundance logtransformed or not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
loadd(plant_rel_abu, sites)

>>>>

---
title: "Supplementary materials"
author: "Fernando Cagua"
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
---

@@

```{r table-species-gain-global, results = 'asis'}
loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_global) %>%
  select(recipient, estimate, statistic, p.value) %>%
  mutate(recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient) %>%
  xtable(caption = "\\label{tab:table-species-gain-global} Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the species level (across communities).") %>%
  print.xtable(sanitize.text.function = function(x) x)
```

```{r table-species-gain-site, results = 'asis'}
loadd(significant_gain_global, significant_gain_site, sites)
glance_table(significant_gain_site) %>%
  inner_join(sites, by = "site_name") %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name)) %>%
  filter(n_sites > 1) %>%
  group_by() %>%
  mutate(site_name = paste(locality_name, land_use, fragment, sep = ' - '),
         recipient = paste0('{\\emph{ ', recipient, '}}')) %>%
  select(recipient, site_name, estimate, statistic, p.value) %>%
  rename(`p value` = p.value,
         `difference` = estimate,
         `plant species` = recipient, 
         `community` = site_name) %>%
  xtable(caption = "Results of testing the alternative hypothesis that the conspecific pollen density in open flowers is greater than the density in bagged flowers. Tests were performed at the community level. Only species present in more than one community are shown.", 
         label= "tab:table-species-gain-site") %>%
  print(sanitize.text.function = function(x) x)
```

```{r table-variation-across-sites, results='asis'}
loadd(consp_self)
consp_self %>%
  anova(test = "Chisq")  %>%
  xtable(caption = 'Analysis of variance of conspecific pollen density in bagged flowers (self pollination rate).  Density were modelled using a quasipoisson distribution. The model suggests that self-pollination rates are species dependent but not across.', 
         label = 'tab:table-variation-across-sites')
```

```{r fig-conspecific-per-site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
loadd(dep_frame, sites)
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

```{r fig-conspecific-per-plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species. Only species present in more than onse site are shown. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name), 
         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
         site_name = str_replace_all(site_name, '_', ' - ')) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Greys")
  })

@@

```{r fig-abundance-logtransformed-or-not, fig.height = 3, fig.cap = "Distribution of plant abundance as (A) raw counts of floral units across communities, and (B) after applying a data transformation in which the counts have been "}
loadd(plant_rel_abu, sites)
